Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
fixed small things
updated app. with zip file sentence
small typo

% Practical implementation
% mention that we do that in batches not full N 
% role of jitter 
% role of clamping
% GPU A100 Nvidia
In practical terms, some care needs to be taken during the implementation, both in terms of memory consumption and numerical stability. For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without need for any further approximations. The computation of the terms in \cref{eq:dual_sparse_post} require the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner by using Cholesky factorization. We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}). 
 We run our experiments GPU clusters equipped with NVIDIA A100 GPUs.

@@

\section{Experiment details}
\label{app:experiments}
%
We provide further details for the experiments presented in the main paper. In tables throughout the paper, we mark the best-performing method/setting by typesetting them boldface. Following this, we check with a two-tailed $t$-test whether the bolded entry significantly differs from the rest. Those not differing from the best performing one with a significance level of 5\% are also bolded. The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification. The 1D regression problem (\cref{fig:teaser}) uses an MLP with two hidden layers (64 hidden units each, with tanh activation), whereas the 2D banana binary classification problem uses an MLP with two hidden layers (64 hidden units each, with sigmoid activation). Both examples use Adam as the optimizer. We include Python notebooks for trying out the models. The illustrative HMC baseline in \cref{fig:banana} (right) was implemented with the help of hamiltorch (\url{https://github.com/AdamCobb/hamiltorch}). We used ten chains with 10,000 samples each and remove 2000 samples as burn-in.

>>>>

% Practical implementation
% mention that we do that in batches not full N 
% role of jitter 
% role of clamping
% GPU A100 Nvidia
In practical terms, some care needs to be taken during the implementation, both in terms of memory consumption and numerical stability. For the former, we batched over the number of training samples, $N$, which keeps the memory consumption in check without need for any further approximations. The computation of the terms in \cref{eq:dual_sparse_post} require the inversion of an $M \times M$ matrix, that we implemented in a numerically stable manner by using Cholesky factorization. We also introduce a small jitter and clip of the GGN matrix for numerical stability where needed (see discussions in \cref{app:experiments}). 
 We run our experiments on GPU clusters equipped with NVIDIA A100 GPUs.

@@

\section{Experiment details}
\label{app:experiments}
%
In this section, we provide further details for the experiments presented in the main paper. In addition to this manuscript, we provide a zip file all the code to reproduce our experiments. In tables throughout the paper, we mark the best-performing method/setting by typesetting them boldface. Following this, we check with a two-tailed $t$-test whether the bolded entry significantly differs from the rest. Those not differing from the best performing one with a significance level of 5\% are also bolded.

The illustrative examples in \cref{fig:teaser,fig:banana} include toy problems for regression and classification. The 1D regression problem (\cref{fig:teaser}) uses an MLP with two hidden layers (64 hidden units each, with tanh activation), whereas the 2D banana binary classification problem uses an MLP with two hidden layers (64 hidden units each, with sigmoid activation). Both examples use Adam as the optimizer. We include Python notebooks for trying out the models. The illustrative HMC baseline in \cref{fig:banana} (right) was implemented with the help of hamiltorch (\url{https://github.com/AdamCobb/hamiltorch}). We used ten chains with 10,000 samples each and remove 2000 samples as burn-in.
